Equalizer\\Programming and User Guide

### 2009-10-19 Developer/ProgrammingGuide/paper.tex
Updates for the new window system interface (see revision 3463).
[ ] May break build
[ ] May break existing applications
[ ] Bugfix
[ ] New Feature
[ ] Cleanup
[ ] Optimization
[x] Documentation

Equalizer provides a generic interface and implementation for the three
most common window systems: AGL, WGL and glX. The interfaces define the
minimal functionality needed to reuse other window system specific
classes, for example the AGL, WGL and glX event handlers. The
implementation derived from these interfaces provides a sample
implementation which honors all configurable window attributes.

@@

    EQASSERT( !_state );
    _state = new VertexBufferState( getObjectManager( ));
    _loadLogo();

    const Config*   config   = static_cast< const Config* >( getConfig( ));
    const InitData& initData = config->getInitData();
    if( initData.useGLSL() )
        _loadShaders();

>>>>

Equalizer provides a generic interface and implementation for the three
most common window systems through the OpenGL specific 
\textsf{eq::GLWindow} class: AGL, WGL and glX. The interfaces define the
minimal functionality needed to reuse other window system specific
classes, for example the AGL, WGL and glX event handlers. The separation 
of the OpenGL calls from the \textsf{OSWindow} permits to implement 
window systems which don't use any OpenGL context and therefore to use a 
different renderer. The implementation derived from these interfaces 
provides a sample implementation which honors all configurable window 
attributes.

@@

    EQASSERT( !_state );
    _state = new VertexBufferState( getObjectManager( ));

    const Config*   config   = static_cast< const Config* >( getConfig( ));
    const InitData& initData = config->getInitData();

    if( initData.showLogo( ))
        _loadLogo();

    if( initData.useGLSL() )
        _loadShaders();
